A deeper look into bug fixes: Patterns, replacements, deletions, and additions

### 2016-02-19 MSRChallenge2016.tex
4 pages!!!

\section{Statement-level mutations}
\begin{table*}
	\centering
	\resizebox{\textwidth}{100pt}{
		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
			\\ \hline

@@

\begin{figure*}[!t] \centering \includegraphics[height=0.3\textheight,
	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many
	bug fixing revisions add/delete statements of the same kind?}
	\label{fig:StmtType} \end{figure*}

>>>>

\section{Statement-level mutations}
\begin{table*}
	\centering
	\resizebox{17cm}{!}{
		\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|} \hline
			&Assert&Break&Continue&Do& For&If&Label&Return&Case&Switch& Synch&Throw&Try&TypeDecl&While
			\\ \hline

@@

\begin{figure*}[!t] \centering \includegraphics[height=0.25\textheight,
	width=0.8\textwidth]{StmtType} \caption{For each kind of statement, how many
	bug fixing revisions add/delete statements of the same kind?}
	\label{fig:StmtType} \end{figure*}
